### 2021-09-20 documentos/pce.tex
WIPTF

\begin{figure} % {{{
\begin{center}
\begin{tikzpicture}[x=0.5cm, y=0.5cm]
% Coordenadas  
\node at (-0.6,0.5) {(a)} ;
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
\begin{scope}[shift={(0,-1)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
\end{scope}
\begin{scope}[shift={(0,-2)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
\end{scope}
\begin{scope}[shift={(0,-3)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
\end{scope}
% Identity
\begin{scope}[shift={(4,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Dephasing
\begin{scope}[shift={(8,0)}]
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Total depolarization
\begin{scope}[shift={(12,0)}]
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
\end{tikzpicture}
\end{center}
	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the positions of the single 
qubit diagrams, so that each square corresponds to a single 
$\tau_{\alpha}$, $\alpha=0,\cdots,3$. The diagrams in 
(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
total depolarization, respectively. In (e) we show a map that erases the two components
$r_1$ and $r_2$ and thus does not correspond to a quantum operation.}
	\label{fig:one:qubit:examples}
\end{figure} % }}}

@@

In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
$\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
\begin{center}
\includegraphics[width=2cm]{2qubits_pce_example}
\end{center}
this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
is not completely positive and therefore is not a quantum channel. In contrast, 
\begin{center}
\includegraphics[width=2cm]{2qubits_pceChannel_example01}
\end{center}
this other example of PCE operation that leaves invariant Pauli components 
$r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
is a quantum channel.

\begin{figure} % {{{
	\centering
	\hfill \hfill
	\includegraphics[height=2.5cm]	{tablero_1qubit}
	\hfill
	\includegraphics[height=2.5cm]{tablero_2qubits}
%	\hspace{1mm}
%	\includegraphics[height=2.7cm]{rho-3q}
	\hfill \hfill \hfill
	\caption{From left to right representations of identity map
	(also PCE operations) of 1 and 2 qubits, respectively.}
	\label{fig:PCE_figs}
\end{figure} % }}}

\begin{figure} % {{{
	\centering
	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
	\caption{1 qubit PCE channels. }
	\label{fig:1qubit_PCEChannles}
\end{figure} % }}}

>>>>

\begin{figure} % {{{
\begin{center}

\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
\def\unitsep{2cm }
% Coordenadas  
\node at (-0.6,0.5) {(a)} ;
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
\begin{scope}[shift={(0,-1)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
\end{scope}
\begin{scope}[shift={(0,-2)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
\end{scope}
\begin{scope}[shift={(0,-3)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
\end{scope}
% Identity
\begin{scope}[shift={(2*1,0)}]
% \begin{scope}[shift={(\unitstep*2,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Dephasing
\begin{scope}[shift={(8,0)}]
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
% Total depolarization
\begin{scope}[shift={(12,0)}]
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
\begin{scope}[shift={(16,0)}]
\node at (-0.6,0.5) {(e)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope}
\end{tikzpicture} % }}}
\end{center}
	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the positions of the single 
qubit diagrams, so that each square corresponds to a single 
$\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
total depolarization, respectively. In (e) we show a map that only erases the component
$r_1$ and thus does not correspond to a quantum operation.}
	\label{fig:one:qubit:examples}
\end{figure} % }}}

@@

% In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
% 1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
% the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
% $\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pce_example}
% \end{center}
% this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
% components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
% is not completely positive and therefore is not a quantum channel. In contrast, 
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pceChannel_example01}
% \end{center}
% this other example of PCE operation that leaves invariant Pauli components 
% $r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
% is a quantum channel. 
% 
% \begin{figure} % {{{
% 	\centering
% 	\hfill \hfill
% 	\includegraphics[height=2.5cm]	{tablero_1qubit}
% 	\hfill
% 	\includegraphics[height=2.5cm]{tablero_2qubits}
% %	\hspace{1mm}
% %	\includegraphics[height=2.7cm]{rho-3q}
% 	\hfill \hfill \hfill
% 	\caption{From left to right representations of identity map
% 	(also PCE operations) of 1 and 2 qubits, respectively.}
% 	\label{fig:PCE_figs}
% \end{figure} % }}}
% 
% \begin{figure} % {{{
% 	\centering
% 	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
% 	\caption{1 qubit PCE channels. }
% 	\label{fig:1qubit_PCEChannles}
% \end{figure} % }}}
